Polyester RNA-seq simulation study

### 2018-02-16 datasets/RNA-Seq/polyester-replicates-benchmarkFDR.Rmd
fixed typo de5 to de10

# # set up parallel backend:
library(BiocParallel)
nCores <- 10
multicoreParam <- MulticoreParam(workers = nCores)
```

@@

>>>>

# # set up parallel backend:
library(BiocParallel)
nCores <- 1
multicoreParam <- MulticoreParam(workers = nCores)
```

@@

plotEffectSize(de10, covname="log2FC")
plotEffectSize(de10, covname="log2FC", DE=FALSE)

plotEffectSize(de10, covname="ind_covariate")
plotEffectSize(de10, covname="ind_covariate", DE=FALSE)
